Weakly Nonlinear MRI: Notes

### 2014-03-03 notes/mri_notes.tex
beginning of multiscale analysis

$\partial_t\partial_z^2\Psi \, + \, J\left(\Psi, \partial_z^2\Psi\right) \, - \, 2\partial_z u_{1y} \, = \, \frac{1}{4\pi}\partial_z\partial_z\Pi \, + \, \frac{1}{4\pi}B_0 \partial_z^3A \, + \, J\left(A, \partial_z^2A\right) \, + \, \frac{1}{\reye}\nabla^2 \partial_z^2 \Psi$ \\

@@

>>>>

$\partial_t\partial_z^2\Psi \, + \, J\left(\Psi, \partial_z^2\Psi\right) \, - \, 2\partial_z u_{1y} \, = \, \frac{1}{4\pi}\partial_x\partial_z\Pi \, + \, \frac{1}{4\pi}B_0 \partial_z^3A \, + \, J\left(A, \partial_z^2A\right) \, + \, \frac{1}{\reye}\nabla^2 \partial_z^2 \Psi$ \\

@@

\section*{Multiscale Analysis}

We now wish to characterize our perturbations in terms of amplitude functions with fast and slow variables. To choose our scalings, we first linearize our equations and find the linear dispersion relation. We then pick spatial and temporal scalings such that the spatial and temporal eigenvalues all appear in the dispersion relation at the same lowest order. \\

Linearizing our four equations, we find a system described by the matrix: \\

%$\left[\begin{smallmatrix}{}s \left(- k_{x}^{2} - k_{z}^{2}\right) - \frac{1}{Re} \left(k_{x}^{4} + 2 k_{x}^{2} k_{z}^{2} + k_{z}^{4}\right) & 2 i k_{z} & \frac{i B_{0} k_{z}}{4 \pi} \left(- k_{x}^{2} - k_{z}^{2}\right) & 0\\\i k_{z} \\left(- \\Omega_{0} q + 2\\right) & s - \\frac{1}{Re} \\left(- k_{x}^{2} - k_{z}^{2}\\right) & 0 & - \\frac{i B_{0} k_{z}}{4 \\pi}\\\\- i B_{0} k_{z} & 0 & s - \\frac{1}{Rm} \\left(- k_{x}^{2} - k_{z}^{2}\\right) & 0\\\\0 & - i B_{0} k_{z} & i \\Omega_{0} k_{z} q & s - \\frac{1}{Rm} \\left(- k_{x}^{2} - k_{z}^{2}\\right)\end{smallmatrix}\right]$

\begin{equation*}
\left[\begin{matrix}
\left(- k_{x}^{2} - k_{z}^{2}\right) - \frac{1}{Re} \left(k_{x}^{4} + 2 k_{x}^{2} k_{z}^{2} + k_{z}^{4}\right) & 2 i k_{z} & \frac{i B_{0} k_{z}}{4 \pi} \left(- k_{x}^{2} - k_{z}^{2}\right) & 0\\

i k_{z} \left(- \Omega_{0} q + 2\right) & s - \frac{1}{Re} \left(- k_{x}^{2} - k_{z}^{2}\right) & 0 & - \frac{i B_{0} k_{z}}{4 \pi}\\

-i B_{0} k_{z} & 0 & s - \frac{1}{Rm} \left(- k_{x}^{2} - k_{z}^{2}\right) & 0\\

0 & - i B_{0} k_{z} & i \Omega_{0} k_{z} q & s - \frac{1}{Rm} \left(- k_{x}^{2} - k_{z}^{2}\right)

\end{matrix}\right] \cdot \left[\begin{matrix}

\Psi \\
u_{1y}\\
A\\
B_{1y}

\end{matrix}\right]
\end{equation*}
